Vampire player characters are discussed in this chapter.

\subsubsection{Vampiric curses}

As vampire legends go, there are several.
It is up to each group to choose what kind creatures vampires are.
It is commonly known, that vampires have told several legends about themselves.
Some have done this to frighten, hurt other vampires, out of self loathing, or to misdirect.
These are represented with vampiric curses.

There are two ways of acquiring vampiric curses.
All vampires gain some set of curses when they shed mortality and become vampires.
This is not players choice, as it is more of what world does to them.
Other way is to lose \humanity{}, as each \humanity{} is paired with some curse.
That curse becomes part of vampires existance, if they fail to follow that ideal.
This is how vampires become more mosterous as time progresses, and struggle for them to keep their humanity.
List of vampiric curses can be found from \ref{ssec:curses}.

When creating vampire character, in addition to normal process, choose at least one key to represent your vampiric nature.
In addition, you need to choose at least one \humanity{} / vampiric curse pair.
Vampiric curse is not active as long you keept your \humanity{} intact.
If you brake against your \humanity{}, you take Instinct damage depending on bad your violation is.
This represent regret vampire feels for their action.
If vampire does not feel regret (players choice), then that \humanity{} is lost forever.
This can be treated as normal key buyoff.
Vampire should have 1-3 \humanities{}, getting new ones without spending advantages on them.
There is limit to this, you can have total of 7 different \humanities{} during \campaign{}.
Losing last one of these, means that there is nothing human left of the vampire and it has become pure monster.
This can be considered death of the character but player might be allowed to play to end of the current \session{}, showing what kind of monster vampire has become.

\subsubsection{Vampiric secrets}
Vampires posses many mystical abilities.
These are represented with special secrets.
Each vampire secret has tiers.
You need to have lower tier power before you can gain higher tier power.
If you use secret in conflict, you can gain bonus dies.
You can gain benefit of maximum of three die per secret used.
It is also possible that using these abilities evade conflict or give vampire enough leverage challenge otherwise insurmountable threat.
It is very common that mortal might not be able to stand against vampire if they do not posses some special skills to face the vampire.
Activating powers give bonus die equal hightest tier of the power.
You can activate power several time for same conflict, but still the maximum amount can be worth of three dies.

\textit{Example: 
Vampire with Virtus wants to drink from mortal. 
Vampire uses his Virtus and overpowers human who tries to resist.
There is no conflict as mortal has no leverge against Vampire.}

\textit{
Example: 
Vampire with Virtus fights against hunter.
Vampire uses his Virtus and human hunter has prepared for this fight.
There is conflict and both roll. Vampire chooses to use his Virtus(II) and uses two from their Vigor pool in order to get 3 bonus die.}

Some secrets might be inherited through the blood and come easily.
Others should not come easily to vampire.
There should always be reason why vampire is able to learn the secret.
Each secret has some requirement for learning but these should be considered as examples.
This is learning that happens by experiencing something that allows vampire to understand something deep hidden inside them.
In addition to learning by experiencing some drastic moment, vampire might try to find a teacher.
Teach ability might be used to allow vampire to learn secret that teacher possess.
If teacher is not found, vampire might start quest for the secret.
Notice, that this means that even though some secret (e.g. Haruspicy(III)) requirement of some other secret (e.g. Haruspicy(II)) also other methods might be used to acquire it.

\pagebreak
\cols{
\SecretVampiricBase{}
\VampiricAbility{}
\VampiricSecret{}
\VampiricKey{}
}

