Mortal characters are good beginning point for any character. 
Mortals in world filled with vampires can be really interesting characters.
These characters can be later updated to vampires, hunters, or thralls as story progresses.

Mortals do not possess unique abilities but can posses unique perspective.
Playing mortal can be great horror experience.
Large amount of vampire fiction is about facing superhuman threat that are out for your blood.

Mortal player characters now typically very little about vampires but more than their peers.
This knowledge puts them them into odds with both vampire and mortal worlds.
Other mortals consider those that know about vampires to be crazy and thus dangerous.
Vampires consider those characters to be nuicanse and possible threat.
However, even though character might know this they cannot return to their previous life, where they were safe as truth is large burden.

Mortal is somehow trying to interact with vampires.
They might have caused death of loved one, or might be mysterious love interest.
Whatever they think about vampires, they are problem.
As they do not know rules that vampires place, they might accidentally release vampire secrets to public.
Worst case might be, that existance of vampires is revealed.
Even asking questions, might be enought to incite violence.

To police, this seems to be stalking and perhaps even attempt on murder.
Even those that mortal convinces, are likely to become ostracised.
What makes things worse, are those vampiric abilities that alter memory, which might start person to question their own sanity.
Also some people these player characters talk to, might be thralls under vampire influence.
Thralls would only try futher isolation of the unwanted individual.


\pagebreak
