For system, we have a few concepts which are be good to know.
This chapter gives short overview.

\para{\nameref{ssec:keys}}
Keys are most important part of the system.
These tell what drives the protagonists.
Keys are also only way to advance protagonist capabilities.

\para{\nameref{ssec:abilities}}
Abilities describe how easily characters can have outcomes they desire.
These are skills, hard earned or innate.
These descibe what character can do, in order to have an affect to the world.

\para{\nameref{ssec:pools}}
These are personal resource of the character.
Abilities relate to some pool.
A pool can be used to improve changes of success when using ability related to that pool.
Pool dwindles as it is being used and can be restored to full by doing something that would refreshing related to that pool.
Differenct characters can have different pools or ways to refresh.

\para{\nameref{ssec:challenges}}
Sometimes situation arises to use ability.
This is called a challenge.
It might test character ability to perform surgery, or forge a sword, for example.

\para{\nameref{ssec:conflict}}
Conflict is two or more characters trying to achieve opposite outcomes utilizing their abilities.
Stakes of the conflict are desided by players of the characters, before determining what result actually takes the place.
It is also possible, that something unexpected disrupts the conflict.
All protagonists have also possibility of extending conflicts where they are, if they end up on losing side.

\para{\nameref{ssec:secrets}}
Each character can also have special abilities.
These can make success with abilities easier, or enable use of some mystical talents.
Characters need to earn their secrets.

\pagebreak

