Every character have Pools which are reserves of strengths of characters.
Players may choose to have their characters spend their pool to boost their attempt while using abilities (Section \ref{ssec:abilities}).
As characters spend their pool, they become more exhausted, physically or mentally.
Eventually characters need to rest, in order to recover their pools.
Thus pools have two numbers, maximum and current.

Every character have these three pools and those represent different resources characters have:
\begin{itemize}
\item{\textbf{Vigor: }Capacity of exerting oneself in physical activity. Someone with low Vigor gets exhausted easily, and will not be able to really commit themselves to this physical activity.}
\item{\textbf{Instinct: }How well one can handle themselves during quick thinking. Someone with low Instinct might be somewhat somewhat slow, and might not be interested on social activities.}
\item{\textbf{Reason: }Shows how well character can push themselves when encountering mental challenges. Someone with low Reason can easily be duped, and is not willing to push themselves when thinking.}
\end{itemize}

Pools also relate to harm character might receive.
Pools are used to heal harm gained and each harm assossiates to one of the pools character has.
Harm is discussed more in (Section \ref{ssec:conflict}).

In addition of healing harm, pools are used to imporve changes on success when using abilities.
This happens when character is determined on compliting the task, and is ready to push themselves little more.

Last use for the pools is activating certain special abilities called secrets (Section \ref{ssec:secrets}).
Using some powers does not come cheaply, and utilizing those will consume something from character.

Pools are used to gain benefits mentioned above.
Pools can also be refreshed.
Characters can refresh their pools by relaxing and letting their guard down.
This also gives story some slow point to see what characters do to relax.
It is also opportunity to something important to happen.

Each pool is refreshed with different condition.
This condition also depends on what the character actually is.
Vampires relax inherently in different way than mortal humans.
Ways each character relaxes is discussed more on character section.
Whenever player wants to protagonist to refresh one or more of their pools, they can describe what protagonist will do in order to relax.
Each pool which condition is met by the way of relaxation is refreshed to full.

\pagebreak
