Abilities define how character can affect world and story around them.
Greater the ability easier it is to use that particular skill to accomplish goals of the character.
Ability score typically represents skill but it can also be luck, or circumstances.

Someone who is not adequate might not even have ability score.
In those cases, character is not able to use that ability.
However, as story goes on, character might acquire new abilities or improve olds.
Acquiring new ability is free, though it means clear shift is character.
Improving ability cost advantages (Section \ref{ssec:keys}), equal to level which it is improved.

Each ability has one pool that relates to it (Section \ref{ssec:pools}).
Pool relating to ability can be utilized to get more out of that ability it is used (Section \ref{ssec:abilities}).

Anatomy of abilities is similar to each other but it is useful to categorize these.
Some categories are not exclusive; same ability might belong into multiple categories.
Abilities are not meant to be exclusive, sometimes it is up to player to choose what ability character uses in certain situation (Section \ref{ssec:abilities}).

\subsubsection{Passive abilities}\label{sssec:passive_abilities}
\hyperref[examples_passive_abilities]{Passive} abilites are special kind of abilities, that every character will have.
These are intrinsic to any sentient being and are last line of defense against threats.
In any situation, passive ability can be used, but it will only help to preserve the character; passive abilites are used only defensively.

\subsubsection{Universal abilities}\label{sssec:universal_abilities}
Some abilities are \hyperref[examples_universal_abilities]{universal} to everyone throughout time.
Every player character has had chance to learn any of these.
Some individuals did not learn these, but still posses basic understanding to acquire these when needed.

\subsubsection{General abilities}\label{sssec:general_abilities}
There are \hyperref[examples_general_abilities]{general} abilites that are common amongst humans, and have existed in humans throughout the history.
However, these are more professional abilities, things that required training to even have access to.
Almost everyone have some of these but having many is quite rare.

\subsubsection{Cultural abilities}\label{sssec:era_abilities}
Some abilites relate to time and place, \textit{i.e.} \hyperref[examples_era_abilities]{cultural}.
These might be easy or difficult to acquire but can easily be out of place to some.
When dealing with centuries old beings, they might posses abilities that are now unheard of and lack some common abilities even in basic level.
Some of the abilities need to be specified, for example \textbf{\AbilityNameReligion} requires to specify what religion it relates to.

\subsubsection{Combat abilities}\label{sssec:combat_abilities}
\hyperref[examples_combat_abilities]{Combat} abilities can be are used to defeat opponent with sheer force.
In general sense, ability describes how well can you fight against an opponent of specific type or survival in situations.
Some combat abilities are general while other are universal.
Abilities with combat in name are to handle opponent of that kind and others are survival in combat situations.

\pagebreak
\subsubsection{Example abilities}
\cols{
\paragraph{\nameref{sssec:passive_abilities}}\label{examples_passive_abilities}

\PassiveAbility

\paragraph{\nameref{sssec:universal_abilities}}\label{examples_universal_abilities}

\UniversalAbility

\paragraph{\nameref{sssec:general_abilities}}\label{examples_general_abilities}

\GeneralAbility

\paragraph{\nameref{sssec:era_abilities}}\label{examples_era_abilities}

\EraAbility

\paragraph{\nameref{sssec:combat_abilities}}\label{examples_combat_abilities}

\CombatAbility
}
\pagebreak
