
Vampiric curses are what define existance of vampire as that of horror.
These both debilitate the vampires and remove them from mortal society.
These curses can effect through supernatural, psychological or sociological.
%% Ei varmaan tartte selittää
%Vampires are entagled with mysticism, so supernatural is easy explanation.
%Sometimes psychosomatic responses can be severe, and so they are if curses exist only in head of vampire.
%Peer pressure and need to belong are basic human needs, and vampire 
Whatever the means are, curses have real tangible effects, even if they come from imagination.

Vampiric curses can be considered to be in layers:
\begin{enumerate}
\item{Universal} 
\item{Setting}
\item{Specific}
\end{enumerate}

Only single curse can be considered universal for vampires in any lore.
This thing defines vampires: lust for blood.
Universal curse is so important, that this book considers it to be always part of vampire.
Other layers are bound to setting.

Setting curse means that these curse comes from setting used.
These come from setting that was chosen when game started.
Typically these are not written in the character sheet, as these should be somewhat common knowledge for players.
If setting is unfamiliar, some printout could be handed to players to help them utilize these. %Todo: hyödyllinen työkalu tätä varten?
Setting curse can be something that applies to every vampire or only some, but it mandated by the setting used.
For example, sunlight might hurt only new vampires or only vampires from certain bloodline.

Specific curses relate to vampires lost humanity.
Each time vampire loses peace of humanity, they also gain curse.
These curses are specific to the vampire, though someone else could have same curses.
Vampires player is one who chooses what curse they gain.
Every player should know these specific curses though as they give interesting opportunities in play.
Player should think what curse is interesting when choosing the curse.
It is better to choose too impactful curse.
If specific curse becomse too debilitating i.e. it removes interesting play instead of adding it, players should discuss about changing it.
In most cases, changing this should not have too big impact, as it can be seen as a phase vampire went through.

Curses presented in this chapter are Setting curses and Specific curses.
Universal curse manifests through certain keys and how pools are refreshed.
Setting curse and Specific curse are not separated.
Any curse presented here can be either.
In some settings no vampire can cross river but in other it affects to just certain vampires.
Curses presented in this book are examples, as there are endless variations on these curses.

These are curses:

\cols{
\CurseSecret{}
}
